### 2017-06-09 Docs/Thesis/docs/appendix/appendixB.tex
New testes scripts in Python and Bash to calc the costFunction of the prototype. Also, at the folder Docs, the thesis text was added, i'm editing it using texstudio.
new advancements on the thesis text

%\newpage
%\renewcommand{\appendixname}{Appendix}

%\appendix

\chapter{Revision of Probability}
\label{ap:revision-probability}

\section{Stochastic Process}

\section{Random variable}

\section{Probability Distribution Function (PDF)}

\section{Cumulative Distribution Function (CDF)}

\section{Expected value, Variance, Mean and Standard Deviation}

\section{Self-similarity}

\section{Heavy-tailed distributions}

\section{Hurst Exponent}

\section{Maximum likelihood function}

\section{Akaike information criterion}

\section{Bayesian information criterion}

\section{Estimation of parameters of stochastic distributions}

\subsection{Linear Regression and Gradient Descendant Algorithm}

\subsection{Maximum likelihood estimation}

\subsection{Others methods}

>>>>

\chapter{Chapter ~\ref{ch:modeling-evaluation} Aditional Plots}
\label{ap:aditional-plots}

\section{CDFs distributions}

\begin{figure}[ht!]
	\centering
	\label{fig:aproximation-original-cdf-bigFlows}
	\subfloat[Chauchy]{
		\includegraphics[width=78mm]{figures/apB/cdf/bigFlows_Logscale_-_Cauchy_aproximation_vs_Original_set}
	}
	\subfloat[Exponential(LR)]{
		\includegraphics[width=78mm]{figures/apB/cdf/bigFlows_Logscale_-_Exponential_aproximation_(linear_regression)_vs_Original_set}
	}
	\hspace{0mm}
	\subfloat[Exponential(Me)]{
		\includegraphics[width=78mm]{figures/apB/cdf/bigFlows_Logscale_-_Exponential_aproximation_(mean)_vs_Original_set}
	}
	\subfloat[Normal]{
		\includegraphics[width=78mm]{figures/apB/cdf/bigFlows_Logscale_-_Normal_aproximation_vs_Original_set}
	}
	\hspace{0mm}
	\subfloat[Pareto(LR)]{
		\includegraphics[width=78mm]{figures/apB/cdf/bigFlows_Logscale_-_Pareto_aproximation_(linear_regression)_vs_Original_set}
	}
	\subfloat[Pareto(MLH)]{
		\includegraphics[width=78mm]{figures/apB/cdf/bigFlows_Logscale_-_Pareto_aproximation_(maximum_likehood)_vs_Original_set}
	}
	\hspace{0mm}
	\subfloat[Weibull]{
		\includegraphics[width=78mm]{figures/apB/cdf/bigFlows_Logscale_-_Weibull_aproximation_vs_Original_set}
	}
	\caption{CDF functions for the approximations of \textit{bigFlows-pcap} inter  packet times, of many stochastic functions.}
\end{figure}

\begin{figure}[ht!]
	\centering
	\label{fig:aproximation-original-cdf-wan}
	\subfloat[Chauchy]{
		\includegraphics[width=78mm]{figures/apB/cdf/wan_Logscale_-_Cauchy_aproximation_vs_Original_set}
	}
	\subfloat[Exponential(LR)]{
		\includegraphics[width=78mm]{figures/apB/cdf/wan_Logscale_-_Exponential_aproximation_(linear_regression)_vs_Original_set}
	}
	\hspace{0mm}
	\subfloat[Exponential(Me)]{
		\includegraphics[width=78mm]{figures/apB/cdf/wan_Logscale_-_Exponential_aproximation_(mean)_vs_Original_set}
	}
	\subfloat[Normal]{
		\includegraphics[width=78mm]{figures/apB/cdf/wan_Logscale_-_Normal_aproximation_vs_Original_set}
	}
	\hspace{0mm}
	\subfloat[Pareto(LR)]{
		\includegraphics[width=78mm]{figures/apB/cdf/wan_Logscale_-_Pareto_aproximation_(linear_regression)_vs_Original_set}
	}
	\subfloat[Pareto(MLH)]{
		\includegraphics[width=78mm]{figures/apB/cdf/wan_Logscale_-_Pareto_aproximation_(maximum_likehood)_vs_Original_set}
	}
	\hspace{0mm}
	\subfloat[Weibull]{
		\includegraphics[width=78mm]{figures/apB/cdf/wan_Logscale_-_Weibull_aproximation_vs_Original_set}
	}
	\caption{CDF functions for the approximations of \textit{wan-pcap} inter  packet times, of many stochastic functions.}
\end{figure}

\begin{figure}[ht!]
	\centering
	\label{fig:aproximation-original-cdf-lan}
	\subfloat[Chauchy]{
		\includegraphics[width=78mm]{figures/apB/cdf/lan_Logscale_-_Cauchy_aproximation_vs_Original_set}
	}
	\subfloat[Exponential(LR)]{
		\includegraphics[width=78mm]{figures/apB/cdf/lan_Logscale_-_Exponential_aproximation_(linear_regression)_vs_Original_set}
	}
	\hspace{0mm}
	\subfloat[Exponential(Me)]{
		\includegraphics[width=78mm]{figures/apB/cdf/lan_Logscale_-_Exponential_aproximation_(mean)_vs_Original_set}
	}
	\subfloat[Normal]{
		\includegraphics[width=78mm]{figures/apB/cdf/lan_Logscale_-_Normal_aproximation_vs_Original_set}
	}
	\hspace{0mm}
	\subfloat[Pareto(LR)]{
		\includegraphics[width=78mm]{figures/apB/cdf/lan_Logscale_-_Pareto_aproximation_(linear_regression)_vs_Original_set}
	}
	\subfloat[Pareto(MLH)]{
		\includegraphics[width=78mm]{figures/apB/cdf/lan_Logscale_-_Pareto_aproximation_(maximum_likehood)_vs_Original_set}
	}
	\hspace{0mm}
	\subfloat[Weibull]{
		\includegraphics[width=78mm]{figures/apB/cdf/lan_Logscale_-_Weibull_aproximation_vs_Original_set}
	}
	\caption{CDF functions for the approximations of \textit{lan-diurnal-pcap} inter  packet times, of many stochastic functions.}
\end{figure}

\section{QQplots}

%\begin{figure}[ht!]
%	\centering
%	\label{fig:aproximation-original-cdf-skype}
%	\subfloat[Chauchy]{
%		\includegraphics[width=78mm]{figures/apB/qq/skype_QQplot_-_Cauchy}
%	}
%	\subfloat[Exponential(LR)]{
%		\includegraphics[width=78mm]{figures/apB/qq/skype_QQplot_-_Exponential(LR)}
%	}
%	\hspace{0mm}
%	\subfloat[Exponential(Me)]{
%		\includegraphics[width=78mm]{figures/apB/qq/skype_QQplot_-_Exponential(Me)}
%	}
%	\subfloat[Normal]{
%		\includegraphics[width=78mm]{figures/apB/qq/skype_QQplot_-_Normal}
%	}
%	\hspace{0mm}
%	\subfloat[Pareto(LR)]{
%		\includegraphics[width=78mm]{figures/apB/qq/skype_QQplot_-_Pareto(LR)}
%	}
%	\subfloat[Pareto(MLH)]{
%		\includegraphics[width=78mm]{figures/apB/qq/skype_QQplot_-_Pareto(MLH)}
%	}
%	\hspace{0mm}
%	\subfloat[Weibull]{
%		\includegraphics[width=78mm]{figures/apB/qq/skype_QQplot_-_Weibull}
%	}
%	\caption{CDF functions for the approximations of \textit{skype-pcap} inter  packet times, of many stochastic functions.}
%\end{figure}

\begin{figure}[ht!]
	\centering
	\label{fig:aproximation-original-cdf}
	\subfloat[Chauchy]{
		\includegraphics[width=78mm]{figures/apB/qq/bigFlows_QQplot_-_Cauchy}
	}
	\subfloat[Exponential(LR)]{
		\includegraphics[width=78mm]{figures/apB/qq/bigFlows_QQplot_-_Exponential(LR)}
	}
	\hspace{0mm}
	\subfloat[Exponential(Me)]{
		\includegraphics[width=78mm]{figures/apB/qq/bigFlows_QQplot_-_Exponential(Me)}
	}
	\subfloat[Normal]{
		\includegraphics[width=78mm]{figures/apB/qq/bigFlows_QQplot_-_Normal}
	}
	\hspace{0mm}
	\subfloat[Pareto(LR)]{
		\includegraphics[width=78mm]{figures/apB/qq/bigFlows_QQplot_-_Pareto(LR)}
	}
	\subfloat[Pareto(MLH)]{
		\includegraphics[width=78mm]{figures/apB/qq/bigFlows_QQplot_-_Pareto(MLH)}
	}
	\hspace{0mm}
	\subfloat[Weibull]{
		\includegraphics[width=78mm]{figures/apB/qq/bigFlows_QQplot_-_Weibull}
	}
	\caption{CDF functions for the approximations of \textit{bigFlows-pcap} inter  packet times, of many stochastic functions.}
\end{figure}

\begin{figure}[ht!]
	\centering
	\label{fig:aproximation-original-cdf-lan}
	\subfloat[Chauchy]{
		\includegraphics[width=78mm]{figures/apB/qq/lan_QQplot_-_Cauchy}
	}
	\subfloat[Exponential(LR)]{
		\includegraphics[width=78mm]{figures/apB/qq/lan_QQplot_-_Exponential(LR)}
	}
	\hspace{0mm}
	\subfloat[Exponential(Me)]{
		\includegraphics[width=78mm]{figures/apB/qq/lan_QQplot_-_Exponential(Me)}
	}
	\subfloat[Normal]{
		\includegraphics[width=78mm]{figures/apB/qq/lan_QQplot_-_Normal}
	}
	\hspace{0mm}
	\subfloat[Pareto(LR)]{
		\includegraphics[width=78mm]{figures/apB/qq/lan_QQplot_-_Pareto(LR)}
	}
	\subfloat[Pareto(MLH)]{
		\includegraphics[width=78mm]{figures/apB/qq/lan_QQplot_-_Pareto(MLH)}
	}
	\hspace{0mm}
	\subfloat[Weibull]{
		\includegraphics[width=78mm]{figures/apB/qq/lan_QQplot_-_Weibull}
	}
	\caption{CDF functions for the approximations of \textit{lan-diurnal-pcap} inter  packet times, of many stochastic functions.}
\end{figure}

\begin{figure}[ht!]
	\centering
	\label{fig:aproximation-original-cdf-wan}
	\subfloat[Chauchy]{
		\includegraphics[width=78mm]{figures/apB/qq/wan_QQplot_-_Cauchy}
	}
	\subfloat[Exponential(LR)]{
		\includegraphics[width=78mm]{figures/apB/qq/wan_QQplot_-_Exponential(LR)}
	}
	\hspace{0mm}
	\subfloat[Exponential(Me)]{
		\includegraphics[width=78mm]{figures/apB/qq/wan_QQplot_-_Exponential(Me)}
	}
	\subfloat[Normal]{
		\includegraphics[width=78mm]{figures/apB/qq/wan_QQplot_-_Normal}
	}
	\hspace{0mm}
	\subfloat[Pareto(LR)]{
		\includegraphics[width=78mm]{figures/apB/qq/wan_QQplot_-_Pareto(LR)}
	}
	\subfloat[Pareto(MLH)]{
		\includegraphics[width=78mm]{figures/apB/qq/wan_QQplot_-_Pareto(MLH)}
	}
	\hspace{0mm}
	\subfloat[Weibull]{
		\includegraphics[width=78mm]{figures/apB/qq/wan_QQplot_-_Weibull}
	}
	\caption{CDF functions for the approximations of \textit{wan-pcap} inter  packet times, of many stochastic functions.}
\end{figure}

\section{Validation}

\begin{figure}[ht!]
	\centering
	\label{fig:correlation-hurst-bigflows-pcap}
	\subfloat[]{
		\includegraphics[width=75mm]{figures/apB/val/bigFlows_Correlation}
		\label{correlation-skype-pcap}
	}
	\hspace{0mm}
	\subfloat[]{
		\includegraphics[width=75mm]{figures/apB/val/bigFlows_Hurst_Exponent}
	}
	\hspace{0mm}
	\subfloat[]{
		\includegraphics[width=75mm]{figures/apB/val/bigFlows_Mean}
	}
	\hspace{0mm}
	\subfloat[]{
		\includegraphics[width=75mm]{figures/apB/val/bigFlows_Standard_Deviation}
		\label{hurst-skype-pcap}
	}
	\caption{Statistical parameters of \textit{bigflows-pcap} and its approximations}
\end{figure}

\begin{figure}[ht!]
	\centering
	\label{fig:correlation-hurst-lan-pcap}
	\subfloat[]{
		\includegraphics[width=75mm]{figures/apB/val/lan_Correlation}
		\label{correlation-skype-pcap}
	}
	\hspace{0mm}
	\subfloat[]{
		\includegraphics[width=75mm]{figures/apB/val/lan_Hurst_Exponent}
	}
	\hspace{0mm}
	\subfloat[]{
		\includegraphics[width=75mm]{figures/apB/val/lan_Mean}
	}
	\hspace{0mm}
	\subfloat[]{
		\includegraphics[width=75mm]{figures/apB/val/lan_Standard_Deviation}
		\label{hurst-skype-pcap}
	}
	\caption{Statistical parameters of \textit{lan-diurnal-pcap} and its approximations}
\end{figure}

\begin{figure}[ht!]
	\centering
	\label{fig:correlation-hurst-wan-pcap}
	\subfloat[]{
		\includegraphics[width=75mm]{figures/apB/val/wan_Correlation}
		\label{correlation-skype-pcap}
	}
	\hspace{0mm}
	\subfloat[]{
		\includegraphics[width=75mm]{figures/apB/val/wan_Hurst_Exponent}
	}
	\hspace{0mm}
	\subfloat[]{
		\includegraphics[width=75mm]{figures/apB/val/wan_Mean}
	}
	\hspace{0mm}
	\subfloat[]{
		\includegraphics[width=75mm]{figures/apB/val/wan_Standard_Deviation}
		\label{hurst-skype-pcap}
	}
	\caption{Statistical parameters of \textit{wan-pcap} and its approximations}
\end{figure}

### 2017-06-09 Docs/Thesis/docs/chapter3.tex
new advancements on the thesis text

%2nd-review
\textbf{Session-layer}: At the session layer, we use a deterministic approach for evaluating times between transferred files (OFF times) and the actual file transference (ON times). It is basically a deterministic ON/OFF model. We choose a deterministic model because in this way we can express diurnal behavior\cite{harpoon-paper}.  \textcolor{red}{<<<<pode mudar, calibrar>>>>} We develop an algorithm called \textit{calcOnOff} responsible for estimating these times. It also determines the number of packets and bytes transferred by each file. Since the on times will serve as input for actual traffic generators, we defined a minimum acceptable time for on periods equals to 100 ms. We did this, first because ON times can be arbitrary smalls, and they could be incompatible with acceptable ON periods for traffic generators. Second, because in the case of just one packet, the ON time would be zero. OFF times, on the other hand, are defined by the constant \texttt{m\_session\_cut\_time}. If the time between packets of the same flow is larger than this, we consider it belonging to a different file, so it is a Session OFF time. In this case, we use the same value of the constant \textit{Request and Response timeout} of Swing\cite{swing-paper} (30 seconds).
The control of ON/OFF periods is made by the \texttt{NetworkFlow} class.

>>>>

%2nd-review
\textbf{Session-layer}: At the session layer, we use a deterministic approach for evaluating times between transferred files (OFF times) and the actual file transference (ON times). It is basically a deterministic ON/OFF model. We choose a deterministic model because in this way we can express diurnal behavior\cite{harpoon-paper}.  We develop an algorithm called \textit{calcOnOff} responsible for estimating these times. It also determines the number of packets and bytes transferred by each file. Since the on times will serve as input for actual traffic generators, we defined a minimum acceptable time for on periods equals to 100 ms. We did this, first because ON times can be arbitrary smalls, and they could be incompatible with acceptable ON periods for traffic generators. Second, because in the case of just one packet, the ON time would be zero. OFF times, on the other hand, are defined by the constant \texttt{m\_session\_cut\_time}. If the time between packets of the same flow is larger than this, we consider it belonging to a different file, so it is a Session OFF time. In this case, we use the same value of the constant \textit{Request and Response timeout} of Swing\cite{swing-paper} (30 seconds) \textcolor{red}{<<<<pode mudar, calibrar>>>>}.
The control of ON/OFF periods is made by the \texttt{NetworkFlow} class.
